A thesis draft

### 2018-10-05 draft.tex
Add additional content about architectural description

In conventional virtualization systems these resources are usually separated 
from the host operating system, providing better isolation but worste 
performance. The ETSI infrastructure, instead, tries with container 
virtualization technology to push for a better NFV responsiveness\todo{Check 
term - I don't think it actually exists}, removing the additional operating 
system (called ``guest'' OS) required by the usual hypervisor-oriented approach.

@@

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openstack}
\paragraph{Openvswitch}
\paragraph{Openbaton}
\paragraph{SDN?}
\end{document}

>>>>

In conventional virtualization systems these resources are usually separated 
from the host operating system, providing better isolation but wrost
performance. The ETSI infrastructure, instead, tries with container 
virtualization technology to push for a better NFV responsiveness\todo{Check 
term - I don't think it actually exists}, removing the additional operating 
system (called ``guest'' OS) required by the usual hypervisor-oriented approach.

To realize the required components, specific tools were suggested in the VNF 
technical proposal: regarding the NFV (network infrastructure) domain 
Docker-Compose was proposed as a viable solution, while to store PEP instances 
docker swarm was described as a possible candidate.

We performed an accured analysis of the tools choosen based on their maturity, 
on the community and on the technical support offered (e.g. user manuals, 
developer documentation), which, at the end, commited us to choose different 
tools from the suggested ones. A detailed description of the architectural 
implementation can be found in chapter~\ref{chap:archimpl}.

@@

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openstack}
\paragraph{Openvswitch}
\paragraph{Openbaton}
\paragraph{SDN?}

\chapter{Architectural implementation}
\label{chap:archimpl}
\end{document}
